Papers

### 2025-03-13 papers.qmd
update

-   de Kock, C., Stafford, T., & Vlachos, A. (2022). [How to disagree well: Investigating the dispute tactics used on Wikipedia](https://arxiv.org/abs/2212.08353). arXiv preprint arXiv:2212.08353.

@@

@@

@@

Stafford, T. and Webb, M. (2004). [Mind Hacks: Tips and Tricks for using your brain](http://www.mindhacks.com/). Sebastapol, CA: O'Reilly.

>>>>

-   De Kock, C., Stafford, T., & Vlachos, A. (2022). [How to disagree well: Investigating the dispute tactics used on Wikipedia](https://arxiv.org/abs/2212.08353). In Y. Goldberg, Z. Kozareva, & Y. Zhang (Eds.), Proceedings of the 2022 Conference on Empirical Methods in Natural Language Processing (pp. 3824–3837). Association for Computational Linguistics. https://doi.org/10.18653/v1/2022.emnlp-main.252

@@

- Lee, J., Zhu, X., Karadzhov, G., Stafford, T., Vlachos, A., & Lee, D. (2025). [Collaborative Evaluation of Deepfake Text with Deliberation-Enhancing Dialogue Systems](https://arxiv.org/abs/2503.04945). arXiv preprint arXiv:2503.04945.

@@

- Stafford, T., Zhu, J., & Dommett, K. (2024, December 31). [Quantifying belief in the rationality of others: the Faith in Reason scale](https://doi.org/10.31234/osf.io/umwxj). Working paper. <https://doi.org/10.31234/osf.io/umwxj>

@@

-   Stafford, T. and Webb, M. (2004). [Mind Hacks: Tips and Tricks for using your brain](http://www.mindhacks.com/). Sebastapol, CA: O'Reilly.
